Characterization of gaps in directly bonded Si compound optics

### 2014-03-05 AO_bondedSi.tex
add particle schematic and text about particles

\section{History of Si direct bonding}
\ref{secHistory}

@@

\subsection{Particles}
Consider the following two conceivable pitfalls in Si-Si direct bonding.  The obvious pitfall is particle contamination.  A single 0.6 $\mu$m particle can create a dark IR bubble from interference.  In the next section we show that smaller bubbles can unacceptably degrade the performance to as low as 10 nm.  In a class 100 cleanroom, the volume density could be as high as $\rho=100$ particles/ft$^3$, with sizes larger than 0.5 $\mu$m.  What we care about is not the volume number density of particles, but the delivered surface flux $F=\rho(D) v(D)$, where v(D) is the average freefall speed of particles, which is a function of particle size.  Figure 5 of Cooper 1986\cite{doi:10.1080/02786828608959094} shows the surface flux (particles cm$-2$ s$-1$) vs. particle size ($\mu$m).  For a change from 1 $\mu$m to 10$-2$ $\mu$m, there is an increase in a factor of $10^4$ in the particle flux expected.  In other words:
$$\log(F) = -2\log(D) + const.$$

So there will be roughly $10^4$ times more 10 nm sized particles than 1 $\mu$m sized particles, which means for every detectable IR bubble, there are thousands more particles that could unacceptably degrade the transmission performance.

@@

\section{Results of infrared spectroscopy of bonded Si pucks}
In this section we describe the spectroscopy of bonded Si pucks.  In some instances IR imaging was available and was leveraged to target IR bubbles.  In other cases the IR imaging was not available or simply ignored, and spectra were taken at random positions on the wafer surface.

\subsection{Constructing the predicted transmission}
We constructed the predicted transmission in the following way.  If IR imaging was unavailable, our optimistic prior belief was simply that the bond should be perfect and indistinguishable from a solitary DSP Si wafer, (i.e. 100\% relative transmission).  For the cases where we had bored gaps of known dimension and fill factors we could predict the transmission with the Fabry-Perot machinery described in section ref{secTheory}, specifically equation \label{eqFP}.  For non-unit fill factor, we simply average 100\% transmission with the predicted gap transmission, weighted by the estimated fill factor.  Notably the meshes we designed were all 50\% fill factor.  No attempt was made to verify the delivered fill factor, but since high precision lithographic processes were employed, we take the design fill factor as gospel.  The depth of the meshes has an associated uncertainty listed in \label{tabbondexper}.  We incorporated the uncertainty in the mesh depth in the following way.  We computed the transmission curve for the 1$\sigma$ lower and upper bounds, and plot a filled band marked as the prediction band.  The uncertainties in the mesh depths were low enough that the band spread includes all intermediate lines of predicted transmission between plus and minus 1$\sigma$.  In cases where the IR imaging was unavailable the mesh position was only coarsely known, so our prediction band had to incorporate our uncertainty about whether or not our measurement beam was on or off or overlapping the mesh border.  If the beam was off the mesh we assumed 100\% relative transmission, so we simply set the lower bound of the predicted transmission to the equivalent of a zero gap.

>>>>

\section{History of Si direct bonding}
\label{secHistory}

@@

\subsection{Particles}

\begin{figure}[htbp]
\centerline{\includegraphics[width=.5\columnwidth]{figs/SiBondParticle.pdf}}
\caption{Schematic of a particle preventing bonding of two Si surfaces\label{figParticle}}
\end{figure}

Consider the following two conceivable pitfalls in Si-Si direct bonding.  The obvious pitfall is particle contamination.  Figure \ref{figParticle} shows a schematic of a particle wedged between two flat Si optical surfaces.  A single 0.6 $\mu$m particle can create a dark IR bubble from interference.  In the next section we show that smaller bubbles can unacceptably degrade the performance to as low as 10 nm.  In a class 100 cleanroom, the volume density could be as high as $\rho=100$ particles/ft$^3$, with sizes larger than 0.5 $\mu$m.  What we care about is not the volume number density of particles, but the delivered surface flux $F=\rho(D) v(D)$, where v(D) is the average freefall speed of particles, which is a function of particle size.  Figure 5 of Cooper 1986\cite{doi:10.1080/02786828608959094} shows the surface flux (particles cm$-2$ s$-1$) vs. particle size ($\mu$m).  For a change from 1 $\mu$m to 10$-2$ $\mu$m, there is an increase in a factor of $10^4$ in the particle flux expected.  In other words:
$$\log(F) = -2\log(D) + const.$$

So there will be roughly $10^4$ times more 10 nm sized particles than 1 $\mu$m sized particles, which means for every obviously detectable IR bubble, there are thousands more particles that could unacceptably degrade the transmission performance.  One key idea that saves the day, is the intuition that the areal fill factor scales at least as fast as $D^2$.  Imagine that the particles serve as miniature tentpoles.  The volume beneath the tentpole looks like a cone.  Since the number density goes down as roughly $D^-2$, (per the equation above) the total area covered by particles might be constant in $log(D)$.  Simply put, the big particles cover just as much area as the small particles, even though there are many more small particles.  It is further conceivable that the areal fill factor attributable to a tent pole particle scales even faster than $D^2$ since surface energy probably scales inversely with distance of the pieces (\`a la VanDerWaals).

It has been shown\cite{1992JEMat..21..669M} that the gases seep through the Si$-$Si interface, so pressure builds around those particles that serve as catalysts.  In this sense, the size of the particle causing an IR bubble cannot be uniquely identified from observations of the extent of IR bubble defects.  In section \ref{secResults} we address the question of the origin of the IR bubbles.  Specifically, are the particles more like \emph{tentpoles}, rigid structures that merely prevent the zippering up of the bond?  Or are the particles more like \emph{catalysts} so that their size is immaterial- the particles merely accelerate the production of gases that bow out the bond?  These are open questions.

@@

\section{Results of infrared spectroscopy of bonded Si pucks}
\label{secResults}
In this section we describe the spectroscopy of bonded Si pucks.  In some instances IR imaging was available and was leveraged to target IR bubbles.  In other cases the IR imaging was not available or simply ignored, and spectra were taken at random positions on the wafer surface.

\subsection{Constructing the predicted transmission}
We constructed the predicted transmission in the following way.  If IR imaging was unavailable, our optimistic prior belief was simply that the bond should be perfect and indistinguishable from a solitary DSP Si wafer, (i.e. 100\% relative transmission).  For the cases where we had bored gaps of known dimension and fill factors we could predict the transmission with the Fabry-Perot machinery described in section ref{secTheory}, specifically equation \ref{eqFP}.  For non-unit fill factor, we simply average 100\% transmission with the predicted gap transmission, weighted by the estimated fill factor.  Notably the meshes we designed were all 50\% fill factor.  No attempt was made to verify the delivered fill factor, but since high precision lithographic processes were employed, we take the design fill factor as gospel.  The depth of the meshes has an associated uncertainty listed in \ref{tabbondexper}.  We incorporated the uncertainty in the mesh depth in the following way.  We computed the transmission curve for the 1$\sigma$ lower and upper bounds, and plot a filled band marked as the prediction band.  The uncertainties in the mesh depths were low enough that the band spread includes all intermediate lines of predicted transmission between plus and minus 1$\sigma$.  In cases where the IR imaging was unavailable the mesh position was only coarsely known, so our prediction band had to incorporate our uncertainty about whether or not our measurement beam was on or off or overlapping the mesh border.  If the beam was off the mesh we assumed 100\% relative transmission, so we simply set the lower bound of the predicted transmission to the equivalent of a zero gap.
